---
title: "Developing Data products Week 4"
author: "Kalpana Rupani"
date: "June 18, 2017"
output: ioslides_presentation
runtime: shiny
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```





## USMLE Score prediction  - Best Model Exploration
This application is intended show the relationship variables within a dataset have when developing a regression model. By adding and removing variables you can explore the coreletation and impact they have in the model.

On the left side of the application you have options to:

Use a subset of the data by adjusting the Science GPA .
Add and remove variables that will be used to determine the best model
Ultimately the model should help you determine which variables are important for USMLE Score. Subsetting the dataset shows the impact the sample has for determining the best model




***
App link: https://krupani.shinyapps.io/predictscore/


***
```{r , echo=FALSE,  message=FALSE, warning=FALSE}
library(shiny)
 
data_full1 <- read.csv("testr.csv",na.strings = c( 0, " "))
data_full <- head(data_full1,79434)
usmle <- data.frame(usmledate= format(as.Date(data_full$USMLE_TEST_DATE, format="%Y.%m.%d"),"%Y"),                            
                    usmlescore=data_full$USMLE_SCORE,finalgrade=data_full$FINAL_GRADE,
                    ogpa=data_full$OVERALL_GPA,sgpa=data_full$SCIENCE_GPA,
                    mcatscore=data_full$MCAT_SCORE,
                    mcatdays=data_full$DAYS_BETWEEN_MCAT_USMLE,
                    priordg_days=data_full$DAYS_BETWEEN_PRIOR_DEGREE_USMLE,
                    subjectcode=data_full$SSBSECT_SUBJ_CODE,
                    priormajor=data_full$PRIOR_MAJOR)
usmle <- na.omit(usmle)
```

```{r , echo=FALSE, message=FALSE, warning=FALSE}

sliderInput("sliderGPA", "What is the Science GPA ?", 0, 5, value = 10)

renderPlot({
               plot(usmle$sgpa, usmle$usmlescore, xlab = "Science GPA",
                    ylab = "USMLE SCORE", bty = "n", pch = 16,
                    xlim = c(1, 5), ylim = c(100, 300))
        
                
})

```


***

Thank You!
